MCC Informativeness - moving agent pilots kids

### 2018-08-06 stats/mcc_novel_pilot_kids.Rmd
fix bug in novel kids 2

Sanity checks.
```{r training performance}
## performance in training and test
d %>%
  group_by(trial_type) %>%
  summarise(n = length(unique(subid)), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 3)

>>>>

Sanity checks.
```{r training performance}
## performance in training and test
d %>%
  group_by(age,trial_type) %>%
  summarise(n = length(unique(subid)), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 3)
